05-exploratory_data_analysis

### 2024-11-27 scripts/05-exploratory_data_analysis.qmd
final version of scripts
add 08-packages_install.R to install all packages in scripts and paper, therefore remove all install packages in other scripts. Changed some preambles and fixed some bugs.

#### Purpose: Explore the analysis data

@@

#### Pre-requisites: analysis data generated in 02-analysis_data

@@

#Install necessary packages
install.packages("tidyverse")
install.packages("arrow")
install.packages("here")
install.packages("ggplot2")
install.packages("patchwork")
install.packages("tidyverse")
install.packages("sf")
install.packages("rnaturalearth")
install.packages("rnaturalearthdata")
install.packages("ggthemes")
install.packages("dplyr")
install.packages("knitr")

>>>>

#### Purpose: Explore the cleaned data

@@

#### Pre-requisites: analysis data generated in 03-cleaned_data

@@
